Manuscript Figures for Genome Biology

### 2018-06-01 manuscript_figures/manuscript_figures.Rmd
Add Figure S7

>>>>

## Uninformative covariate impact on simulations

Here we'll contrast the results of informative and uninformative covariates 
on the yeast simulation (null and DE sample size 5).

```{r FigureS7}
objects <- list.files( path, recursive=TRUE, pattern="rds", full.names=TRUE )
resfile <- objects[grepl("yeast", objects) & 
                   grepl("de5|null5", objects)] 
de5 <- readRDS(file=resfile[grepl("de5", resfile) & !grepl("uninf", resfile)])
de5_uninf <- readRDS(file=resfile[grepl("de5", resfile) & grepl("uninf", resfile)])
null5 <- readRDS(file=resfile[grepl("null5", resfile) & !grepl("uninf", resfile)])
null5_uninf <- readRDS(file=resfile[grepl("null5", resfile) & grepl("uninf", resfile)])
excludeSet <- c("unadjusted", "bl-df02", "bl-df04", "bl-df05")

res5d <- plotsim_standardize(de5, alpha = seq(0.01, 0.10, 0.01))
res5d_u <- plotsim_standardize(de5_uninf, alpha = seq(0.01, 0.10, 0.01))
res5n <- plotsim_standardize(null5, alpha = seq(0.01, 0.10, 0.01))
res5n_u <- plotsim_standardize(null5_uninf, alpha = seq(0.01, 0.10, 0.01))

pa <- plotsim_average(res5n_u, met="TNR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
        expand_limits(y=.7) +
        xlab("") +
        ggtitle("")

pb <- plotsim_average(res5n, met="TNR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
        theme(legend.position="none", plot.title = element_text(hjust = 0.5))+
        expand_limits(y=.7) +
        xlab("") +
        ggtitle("")

pc <- plotsim_average(res5d_u, met="FDR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
        theme(legend.position="none") +
        expand_limits(y=0.2) +
        xlab("") +
        ggtitle("")

pd <- plotsim_average(res5d, met="FDR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
        theme(legend.position="none") +
        expand_limits(y=0.2) +
        xlab("") +
        ggtitle("")

pe <- plotsim_average(res5d_u, met="TPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
        theme(legend.position="none") +
        expand_limits(y=0.33) +
        ggtitle("")

pf <- plotsim_average(res5d, met="TPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
        theme(legend.position="none") +
        expand_limits(y=0.33) +
        ggtitle("")

leg <- get_legend(pa)
pa <- pa + theme(legend.position="none", plot.title = element_text(hjust = 0.5))

FigT  <- plot_grid(pa, pb, ncol = 2, 
          #labels = LETTERS[1:2], 
          label_size = 20)

FigB  <- plot_grid(pc, pd, pe, pf, ncol = 2, 
          #labels = LETTERS[3:6], 
          label_size = 20)

Fig <- ggdraw() +
  draw_plot(FigT + ylab("") + xlab(""), 0, 0.64, 1, 0.3) +
  draw_plot(FigB + ylab("") + xlab(""), 0.005, 0, 1, 0.6) +
  draw_plot_label(c("Uninformative Covariate", "Informative Covariate"), 
                  c(0.14, 0.64), c(1,1), c(0,0), size = 15) +
  draw_plot_label(c("Null Simulation", "DE Simulation"), 
                  c(0.36, 0.37), c(0.96,0.62), size = 13)

Fig <- plot_grid(Fig, leg, ncol = 2, rel_widths = c(1, 0.2))
Fig
ggsave(file.path(outdir, "FigureS7.pdf"), width=10, height=11)
